Towards a classification framework for social machines

### 2013-02-24 latex/paper_new.tex
working on 4.3

\subsubsection{Users and Roles}
The first set of constructs pertain to the human participants of
social machines and the way(s) participants are organised within them.
First, whether participants consistute members of the general public,
or are of a specific demongraphic, external group or organisation,
occupation, or of a particular expertise.  Second, pertain to how
constrained interaction is among members of the machine (lack of
\emph{autonomy}), and the degree to which participants are anonymous.

>>>>

\subsubsection{Users and Roles}
The first set of constructs pertain to the human participants of
social machines and the way(s) participants are organised within them.
One construct identifies whether participants constitute members of
the general public, or are of a specific demongraphic, external group
or organisation, occupation, or of a particular expertise.  Two
constructs, \emph{autonomy} and \emph{anonymity} pertain to the degree
to which interaction is constrained among participants, and to the
degree to which participants' identities are used and disclosed within
the machine. The final two constructs pertain to the roles: first,
as to whether multiple roles are pre-differentiated by the machine or
whether all participants essentially initially assume the same role,
second whether roles (pre-defined or emergent) are archical.
